Clinical advancement forecasting \thanks{\textit{\underline{Citation}}: \textbf{TBD}}

### 2024-04-14 paper/paper.tex
Minor updates

An important question, that remains difficult to answer, is how much target prioritization methods like the one explored in this study can improve the efficiency of drug discovery. One 2018 estimate suggests that improving success rates from phase 1 to approval by 1.4x (from 9.6\% to 13.8\%) would reduce the median R\&D cost for a \textbf{single drug} by \$480 million USD \cite{PMID:32125404}. If a 2x increase in success rates from phase 1 to approval could be expected when pursuing only genetically validated TD pairs \cite{Nelson2015-eg}, then this would increase to a \$686 million cost savings per drug. Pushing that even further to a 3x or 4x increase by incorporating more lines evidence, as we have done here, would suggest a per-drug cost savings of \$1.03 billion and \$1.37 billion, respectively. These savings would only be realized for drugs tested against targets and diseases with sufficient supporting evidence; however, we show in Section~\ref{sec:results_opportunities} there are more than 8,000 such opportunities (i.e. untested, present-day TD pairs) where at least a 3x improvement in success rates could be expected.

>>>>

An important question, that remains difficult to answer, is how much target prioritization methods like the one explored in this study can improve the efficiency of drug discovery. One 2018 estimate suggests that improving success rates from phase 1 to approval by 1.4x (from 9.6\% to 13.8\%) would reduce the median R\&D cost for a \textbf{single drug} by \$480 million USD \cite{PMID:32125404}. If a 2x increase in success rates from phase 1 to approval could be expected when pursuing only genetically validated TD pairs \cite{Nelson2015-eg}, then this would increase to a \$686 million cost savings per drug. Pushing that even further to a 3x or 4x increase by incorporating more lines evidence, as we have done here, would suggest a per-drug cost savings of \$1.03 billion and \$1.37 billion, respectively. These savings would only be realized for drugs tested against targets and diseases with sufficient supporting evidence; however, we show in Section~\ref{sec:results_opportunities} that there are more than 8,000 such opportunities (i.e. untested, present-day TD pairs) where at least a 3x improvement in phase 2 success rates could be expected.
